Nanophotonic Computational Design

### 2013-02-25 defense/pres3.tex
Final.

\I  \bold{Problem}: How to overcome the apparent trade-off 
    between manufacturability ($z$) and performance ($x$)?
\pause
\I  Realized that there do exist some $x$ (fields)
    which result from manufacturable $z$ (structures)
    \BI These can be produced via simulation
    \I  However, it's not useful to ask the user to choose such $x$ \EI
\pause
\I  Therefore, a \emph{useful} tool would optimize for \emph{both} $x$ and $z$
\nextpage

@@

\I  Problem statement in physics language
\threeDfig{3Db_wgc_te}
\I  Input mode is excited using current source ($b_i$ or $-i\omega J$)
\I  Output mode is enforced using overlap integrals
    ($c_{ij}\T x_i$ or $\int \hat{E_{ij}} E$)
\nextpage

@@

@@

\I  \bold{Result}: Stable wavelengths available even up to $905$K shifts!
\threeDfig{analysis_temp_shift2}
\pause
\I  $\Delta T = 905$K point marks refractive index shift from 3.5 to 3.67 (huge!)
\pause
\I  Potentially means that networks with no need for thermal tuning are possible
    \BI Occurs when thermal robustness $>$ thermal swing \EI
\nextpage

@@

\oursection{Conclusion}
\footnotetext{$^\ast$maybe}
\I  How to design any$^\ast$ linear multi-mode nanophotonic device
    \BI using the full parameter space
    \I  simply by describing its operation \EI
\pause
\I  Our method results in designs which are
    \BI extremely compact
    \I  manufacturable \EI
\pause
\I  Devices can be designed which are robust to
    \BI wavelength shifts
    \I  thermal shifts 
    \I  fabrication error \EI
\oursection{Acknowledgements}
\begin{quote}
Not unto us, O Lord, not unto us, \\
But to Your name give glory, \\
Because of Your mercy, \\
Because of Your truth. (Psalm 115:1)
\end{quote}
\stepwise{
\step{Mom, Dad, }
\step{Jennifer, }
\step{Eli, }
\step{Seth, Lieven, Kelley,}
\step{Shanhui, Mark,}
\step{David,}
\step{Jelena,}
\step{Stephen,}
\step{Maria, Yiyang, Szu-lin, Gary,}
\step{JVgroup,}
\step{Owen, Paul,}
\step{Wonseok,}
\step{Ingrid,}
\step{Church family,}
\step{Sandy, Josiah}

>>>>

\I  \bold{Problem}: How to overcome the apparent trade-off 
    between manufacturability ($z$) and performance ($x$)?
\pause
\I  Realized that there do exist some $x$ (fields)
    which result from manufacturable $z$ (structures)
    \BI These can be produced via simulation
    \I  However, it's not useful to ask the user to choose such $x$ \EI
\pause
\I  \bold{Realization}: A \emph{useful} tool must optimize for \emph{both} $x$ and $z$
\nextpage

@@

\I  Problem statement in physics language
\threeDfig{3Db_wgc_te}
\I  Input mode is excited using current source ($b_i$ or $-i\omega J$)
\I  Output mode is enforced using overlap integrals
    ($c_{ij}\T x_i$ or $\int \hat{E}_{ij} E$)
\nextpage

@@

\I  Broadband design still high efficiency 
\I  Efficiency (1310 nm and 1550 nm): 84.2\%, 82.3\% (0.09\%, 1.41\%)
\medfig{top_wdm}

@@

\I  \bold{Result}: Stable wavelengths available even up to $\sim1000$K shifts!
\threeDfig{analysis_temp_shift2}
\pause
\I  $\Delta T = 905$K point marks refractive index shift from 3.5 to 3.67 (huge!)
\pause
\I  Potentially means that networks with no need for thermal tuning are possible
    \BI Occurs when thermal robustness $>$ thermal swing \EI
\nextpage

@@

\oursection{Conclusion}
\footnotetext{$^\ast$maybe}
\I  How to design any$^\ast$ linear multi-mode nanophotonic device
    \BI using the full parameter space
    \I  simply by describing its operation \EI
\pause
\I  Our method results in designs which are
    \BI extremely compact
    \I  manufacturable \EI
\pause
\I  Devices can be designed which are robust to
    \BI wavelength and temperature shifts 
    \I  fabrication error \EI
\oursection{Acknowledgements}
\begin{quote}
Not unto us, O Lord, not unto us, \\
But to Your name give glory, \\
Because of Your mercy, \\
Because of Your truth. (Psalm 115:1)
\end{quote}
\stepwise{
\step{Mom, Dad, }
\step{Jennifer, }
\step{Eli, }
\step{Seth, Lieven, Kelley,}
\step{Shanhui, Mark,}
\step{David,}
\step{Jelena,}
\step{Stephen,}
\step{Maria, Yiyang, Szu-lin, Gary,}
\step{JVgroup,}
\step{Owen, Paul,}
\step{Wonseok,}
\step{Ingrid,}
\step{Church family,}
\step{Sandy, Josiah}
